\textbf{BibTrek Prototype: A Graph Visualization Tool and Search Engine for Cybersecurity Papers}

### 2019-07-26 article/article.tex
typos

\section{Evaluation}
#Yet to be written

>>>>

\section{Evaluation}
\subsection{Tests}
We have tested our application for a vast array of author and publication queries whilst locally running Neo4J using a Lenovo T400 computer with the following specs:
\begin{itemize}
\item \textbf{OS:} 64-bit Ubuntu 18.04.2 LTS GNU/Linux 
\item \textbf{CPU:} Intel Core 2 Duo P8700 @ 2.534GHz 
\item \textbf{GPU:} Intel Mobile 4 Series Chipset
\item \textbf{RAM:} 4096MB @ 1066Mhz 
\end{itemize}
BibTrek successfully processed and inserted all nodes and relations into the Neo4J database. We were able to search for any added data with ease. However, the data retrieved from the DBLP database might present a variable number of field attributes. Since we are following a fixed attribute structure for our node data, some of these fields are ignored. Future versions should consider adding these fields dynamically, we further these considerations on the Future Work section of this article.
\subsection{Functionalities}
At the current moment we can choose only to retrieve data from the DBLP publication. Nonetheless, future versions will include an option to query the ArXiV library, IEEE Xplore and any combination of these. Choosing the DBLP option we are able to pick whichever option suits our interests the most. At the current time we are able to query by author's name, author's publications and publication title. Once queried, BibTrek presents us the data that it has been able to retrieve. The user is then given the option to mark whichever of the retrieved information will be stored in the Neo4J graph database. The marked options are then stored on the graph with their appropriate relations. It is possible at any given moment to abort any of the above mentioned procedures.

\section{Future Work}
The reader of this article has to keep in mind that this project was developed in one month throughout the writer's internship with INESC-ID. Because of this there are many aspects of the current BibTrek implementation that ought to be further engineered and developed. To begin with, one of the obvious aspects to further develop would be to fetch information from more than one web based library. At the current moment only the DBLP is being used. Finally, while the ArXiV API is free to use, IEEE Xplore requires the use of a key attributed to its developers. Another aspect that should be considered is the use of dynamic attributes since, at the moment, any block of data that is fetched has some of its attributes unused because, we adhere to a fixed attribute standard when adding data to the database. At the current moment the only nodes being added to the database are either Authors or Publications. We should consider adding Companies, Foundations, Organizations, Universities and other Institutions that authors are or have been linked with in the past, Keywords/Subjects and any other relevant information for the reader. It is worth being said that nodes being created ought to be the most common set of information between the data that is being stored in the different databases that BibTrek will be using. Finally, along with more diverse nodes, each one of them should have a vast array of arguments in order to better categorize the information being added. Furthermore, at the current moment BibTrek allows the user to add duplicated information. Obviously a check should be added in the Java code that compares if the information that is trying to be added has been put there already. Finally, we are not able to query our Neo4J graph database through the terminal console. The work to be done regarding this topic is developing the option of querying the database through a user input choice from a vast array of specific functions that manipulate the information present there, displaying relevant information about the current status of the data to the user we the intent on aiding its research process. An example of a query would be getting the most referenced paper by all the papers presently on the database with respect to a certain subject or given the current paper title that references one of the said papers.
